### 2015-07-07 narrative/enabling_tech.tex
edits for 1.2

  From the user perspective, something like the
{\bf ADIOS}~\cite{lofstead:2009:adaptible} API offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This affords writing to a single output API while shifting from
writing to a file system to operating on the data using in situ techniques, without
changing the source code. ADIOS has proven effective for writing to POSIX file
systems, data staging systems~\cite{zheng:2010:predata,docan:2010:dataspaces,oldfield:2006:nessie}, workflow
systems~\cite{Dayal:2014:flexpath}, and even through the WAN network 
Part of this project's goals seeks to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users. We will utilize DataSpaces~\cite{docan:2010:dataspaces} to 
 further integrate the I/O (ADIOS) layer with the storage layer (Sirocco).
%
% 
%They offer a way to request data set portions
%from a one component by the next componet in a data flow. In DataSpaces case,
%the data transfer does not have to correspond to the data from a single
%process.  Instead, DataSpaces will determine where the data is and issue
%requests to pull the data from the source to the sink in an on demand process.

>>>>

From the user perspective,
{\bf ADIOS}~\cite{lofstead:2009:adaptible} offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This flexibility allows users to shift from writing data to a file system
to operating on data with in situ techniques without changing the source code.
ADIOS has proven effective for writing to POSIX file
systems, data staging systems~\cite{zheng:2010:predata,docan:2010:dataspaces,oldfield:2006:nessie}, workflow
systems~\cite{Dayal:2014:flexpath}, and even through the WAN network 
Part of this project's goals are to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users. We will utilize DataSpaces~\cite{docan:2010:dataspaces} to 
further integrate the I/O (ADIOS) layer with the storage layer (Sirocco).
%
% 
%They offer a way to request data set portions
%from a one component by the next componet in a data flow. In DataSpaces case,
%the data transfer does not have to correspond to the data from a single
%process.  Instead, DataSpaces will determine where the data is and issue
%requests to pull the data from the source to the sink in an on demand process.
